%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Presentations}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
%\vspace{-0.3cm}
%\begin{small}\textit{* presenting author; \textsuperscript{+} mentored undergraduate}\end{small}

%-------------------------------------------------------------------------------
\cvsubsection{Invited Talks}
%-------------------------------------------------------------------------------

\begin{cvpubs}

\cvpub {23/04/2026. \textbf{Relational Information Towards a New Kind of Information in Quantum Mechanics}.Weekly Meeting Departamento de Fisica Teorica, Universidad Complutense de Madrid, Madrid, Spain.}


\cvpub {19/04/2026. \textbf{Entanglement, fatti relativi e il significato di "informazione" nell' interpretazione relazionale della meccanica quantistica}. Il Paradosso della realta' fisica 1985 -225, University of Urbino, Cesena, Italy.}

\cvpub {11/03/2026. \textbf{Relational Information Towards a New Kind of Information in Quantum Mechanics}. University of Jagellonian, Krakow, Poland.}

\cvpub {05/03/2026. \textbf{Relational Information Towards a New Kind of Information in Quantum Mechanics}. Katedra Teorii Prawdopodobieństwa i Statystyki WMiI UŁ wraz z Oddziałem Łódzkim PTM, University of Lodz, Lodz, Poland.}

\cvpub {17/12/2025. \textbf{Once Again on von Neumann entropy: is Always The Case That von Neumann Entropy Correspond to Thermodynamic Entropy?}. Workshop: Philosophical Foundations of Thermodynamics, Ponteficia Universidad Católica De Valparaíso, Valparaíso, Chile.}


\cvpub {20/11/2025. \textbf{Relational Information: Towards a New Type of Information in Quantum Mechanics}. Invited talk: Physics meets Philosophy in Vienna, Institute for Quantum Optics and Quantum Information, Vienna, Austria.}
    
  %  \cvpub{Spring 2018. \textit{A guest lecture for a course}. Guest Lecture, Name of Course, University.}
    
   % \cvpub{Spring 2018. \textit{A different invited talk that I gave}. Invited talk: Event I Presented At, City, State.}
\end{cvpubs}

%-------------------------------------------------------------------------------
\cvsubsection{Contributed Presentations}
%-------------------------------------------------------------------------------

\begin{cvpubs}

\cvpub{\textbf{Relational Information Towards a New Kind of Information in Quantum Mechanics}
\\
22/07/2026. 
Asian Philosophy of Science Association (APSA) Conference 2026, NTU Singapore, Singapore}

\cvpub{\textbf{Segal Entropy and the notion of Information}
\\
09/05/2026. 
Workshop: Perspectives on the Foundations of Information Theory and Statistical Mechanics Università della Svizzera Italiana, Lugano, Switzerland}

 \cvpub{\textbf{ From ‘It from Bit’ to Relational Quantum Mechanics: Wheeler and Rovelli in Historical and Conceptual Perspective } 
    \\
    10/12/2025. Towards a Quantum Culture: The Different Interpretations of Quantum Mechanics, Workshop of the Italian Society for the History of Physics,  Università Studi di Milano, Milano, Italy}

 \cvpub{\textbf{Relational Quantum Mechanics and (Soft) Perspectivism} 
    \\
    16/10/2025. Philosophy of Science Conference on the Occasion of the 140th Anniversary of Niels Bohr’s Birth, Sofia, Bulgaria}

    \cvpub{\textbf{ A (quasi)-Mathematical Theory of Public Language }  
    \\
    12/08/2025. 46th International Wittgenstein Symposium, Kirchberg am Wechsel, Austria}

\cvpub{\textbf{Progress Crucial Realism }  
    \\
    11-13/06/2025. SILFS Postgraduate Conference, Turin, Italy}

   \cvpub{\textbf{From Shannon to Von Neumann: A partial understanding of Information }  
    \\
    18/09/2024. XLIV National Congress of SISFA, Firenze, Italy}


    \cvpub{\textbf{The Forbidden Realm for the Maxwell’s Demon: Information Entropy}
    \\
    09/09/2024. Synergia PhD Research Symposium - Charting New Frontiers in Research}



    \cvpub{\textbf{Levels of Abstraction as family resemblances: from the classical to the quantum mechanical representation of reality  }  
    \\
    12/08/2024. 45th International Wittgenstein Symposium, Kirchberg am Wechsel, Austria}


    \cvpub{\textbf{Exploring Quantum Information Processes through the Method of Abstraction: Quantum-Levels of Abstraction}  
    \\
    04/08/2024. XXV World Congress of Philosophy, Rome, Italy }

    \cvpub{\textbf{Fearing Bitcoin}  
    \\
    03/08/2024. XXV World Congress of Philosophy, Society Section SILFS, Rome, Italy }

    


    \cvpub{\textbf{Method of Abstraction: A Tentative Exploration of Quantum Information Processes} 
    \\
    07/12/2023. Seminar organized by SYNERGIA the Research Group in Logic, Language, Cognition, History and Phylosophy of Science, Università di Urbino Carlo BO, Urbino, Italy. }

    \cvpub{\textbf{Contextuality of Abstraction}
    \\
    31/03/2023. Seminar organized by the professor of Philosophy of Mind Silvano Zipoli Caiani. University of Firenze, Firenze, Italy.}

    \cvpub{\textbf{Una breve panoramica della Filosofia dell’informazione: dall’informazione classica all’informazione quantistica}
    \\
    10/11/2022. Seminar organized by the student university association Gavagai. Pisa, Italy.}

   
\end{cvpubs}


\cvsubsection{Poster Presentations}

\begin{cvpubs}
\cvpub{\textbf{Progress Crucial Realism}
    \\
    29/08/2025. 10th biennial meeting of the European Philosophy of Science Association. Groningen, Netherlands.
     }


     \cvpub{\textbf{Progress Crucial Realism}
    \\
    01/07/2025. Foundation2025. Gdańsk, Poland.
     }

    \cvpub{\textbf{Shannon's approach to quantum information}
    \\
    14/10/2024. Probability in Computer Science (PICS) 2024. Copenhagen, Denmark.
     }
\end{cvpubs}

\cvsubsection{Public Presentations}

\begin{cvpubs}
\cvpub{\textbf{Certo per Incerto: Quanta Informazione}
    \\
    20/04/2026. Facoltà di Teologia di Lugano. Lugano, Switzerland.
     }


\end{cvpubs}

