%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Publications}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------

%---------------------------------------------------------
\cvsubsection{Published}
%---------------------------------------------------------

\begin{cvpubs}

\cvpub{Vincenzo Fano, Niccolò Covoni. 2026. Phenomenological Elements in Carnap's \textit{Aufbau}: The Epistemological Role of Sensible Intuition, in \textit{Sophia}, XVIII (2026-1), 29-51. \href{https://journal.sophiauniversity.org/wp-content/uploads/2026/06/Fano-Covoni-da-Sophia-2026-1.pdf}{Open access PDF}.}

\cvpub{Niccolò Covoni, Marco Sanchioni. 2026. Relational Information Towards a New Kind of Information in Quantum Mechanics in \textit{Foundations of Physics}, 56(1): 14.}

\cvpub{Niccolò Covoni, Vincenzo Fano, Marco Sanchioni. 2025. Relational Quantum Mechanics and (Soft) Perspectivism in \textit{Foundations of Physics}, 56(1): 6.}

\cvpub{Niccolò Covoni, Carlo Rovelli. 2025. Tractatus Quanticus, https://arxiv.org/abs/2512.06034}

\cvpub{Niccolò Covoni, Gino Tarozzi. 2025. Tra realismo e neopositivismo:l’eredità di Ludovico Geymonat e Evandro Agazzi nella filosofia della
scienza italiana in \textit{Bíos theôrêtikós e bíos praktikós. Studi offerti a Fabio Minazzi per i suoi settant’anni}, Mimesis Edizioni, Milano.}

\cvpub{Niccolò Covoni, Flavia Marcacci, Gino Tarozzi. 2025. From neo-idealistic historicism to Geymonat’s materialistic and Agazzi’s objectivistic realism: the roots of the Italian philosophy of science, in \textit{BIOETHICS UPDATE}, 11(2), https://doi.org/10.24875/BUP.25000013.}

\cvpub{Niccolò Covoni. 2025. From Shannon to Von Neumann: A partial understanding of Information, in \textit{Atti del XLIV Congresso Nazionale SISFA - Firenze 2024}, 43(10), 89-94.}

\cvpub{Niccolò Covoni, Giovanni Galli. 2025. A (quasi)-Mathematical Theory of Public Language, in Proceedings 46th International Wittgenstein Symposium 2025.}

\cvpub{Niccolò Covoni, Giovanni Macchia, Davide Pietrini and Gino Tarozzi. 2025. Non-standard realistic models of quantum phenomena and new forms of complementarity, in \textit{Models and Representations in Science, edited by Hans-Peter Grosshans. Comptes Rendus de l’Académie Internationale de Philosophie des Sciences} 3, 39-54.}

\cvpub{Niccolò Covoni, Alberto Corti, Vincenzo Fano. 2024. A Model-Based form of Naturalised Metaphysics, Revista Portuguesa de Filosofia, 80(4), 783-818.}

\cvpub{Niccolò Covoni, Gino Tarozzi. 2024. Empiricism and Realism Reconciled in Agazzi’s Conception of Scientific Objectivity, Distinctio: Journal of Intersubjective Studies, Zagreb, 3(1), 47-55.}

 \cvpub{Niccolò Covoni, Silvano Zipoli Caiani. 2024. Levels of Abstraction as family resemblances from the classical to the
quantum mechanical representation of reality in Proceedings 45th International Wittgenstein Symposium 2024 "Facets of Reality — Contemporary Debates"}

\noindent\begin{minipage}{\linewidth}
\cvpub{Marco Ciardi, Niccolò Covoni. 2024. La profezia di Ada Lovelace. L'intelligenza artificiale prima di Turing. On Filosofia dell'intelligenza artificiale. Sfide etiche e teoriche, Il Mulino, Bologna, ISBN: 978-88-15-38737-0}
\par\end{minipage}

\cvpub{Marco Ciardi, Niccolò Covoni. 2023. Dalla Mano Per Calcolare ai Calcolatori per la Mano. On L'Origine del Pensiero Numerico, Guide Museo e Istituto fiorentino di Preistoria, ISBN: 979-12-80445-06-3.}

   % \cvpub{\textbf{Name, Y}, Author Two, Author Three. 2016. Title of our other fancy paper, which also has a very long name so that the citation goes onto the next line. Journal, 1(1): 1000-1100.}%
\end{cvpubs}

% %---------------------------------------------------------
\cvsubsection{In Review}

\cvpub{Niccolò Covoni,  Hanna Podsędkowska, Rafa\l \space Wieczorek. 2026. Segal Entropy and Relational Information}

\cvpub{Alberto Corti, Niccolò Covoni, Vincenzo Nespeca, Marco Sanchioni. 2026. Progressive Scale Realism A naturalized realistic interpretation of Spin}


\cvpub{Niccolò Covoni, Marco Sanchioni. 2026. Relationality without Agents:
Quantum Correlations and the Limits of QBism}

\cvpub{Niccolò Covoni, Marco Sanchioni. 2026. Progress Crucial Realism}

\cvpub{Niccolò Covoni, Marco Sanchioni. 2026. Entanglement, Relative Facts, and the Meaning of Information in Relational Quantum Mechanics}

\cvpub{Niccolò Covoni, Marco Sanchioni. 2026. Progress-Crucial Realism
Toward a Selective Meta-Ontology}

\cvpub{Niccolò Covoni, Marco Sanchioni. 2026. From “It from Bit” to Relational Quantum Mechanics: Wheeler, Rovelli, and the Relational Turn in Quantum Foundations}




\cvsubsection{Under Contract}

\cvpub{Carlo Rovelli, Niccolò Covoni, Andrea Di Biagio. 2026. Tractatus Quanticus, John Wiley \& Sons Ltd}







% %---------------------------------------------------------

\begin{cvpubs}
   

    %\cvpub{Manuscript 2}%
\end{cvpubs}

% %---------------------------------------------------------
%\cvsubsection{In Prep}%
% %---------------------------------------------------------

%\begin{cvpubs}
%\small \color{black}
  %  \cvpub{Manuscript 1}

   % \cvpub{Manuscript 2}
%\end{cvpubs}

% %---------------------------------------------------------
